Data-driven Reduction of Multiscale Stochastic Dynamical Systems

### 2014-07-14 reducible_SDE/paper/paper_draft.tex
Added paper draft

\begin{equation}
\begin{aligned}
dx &= adt + dW_1\\
dy &= -\frac{y}{\epsilon} dt + \frac{1}{\sqrt{\epsilon}} dW_2
\end{aligned}
\end{equation}

@@

We want to emphasize the link between multi scale SDEs and NIVs: NIVs rescales the variables so that the ``fast'' variables become small

saturation time of SDE has to be smaller than the timescales

Let $y = \frac{z}{\sqrt{\epsilon}}$. Then
\begin{equation}
\begin{aligned}
dx &= adt + dW_1\\
dz &= -\frac{z}{\epsilon} dt +  dW_2
\end{aligned}
\end{equation}

@@

@@

Empirical configuration/demonstration of the method, how to use the analysis to set the parameters in the algorithm

@@

>>>>

\begin{equation} \label{eq:multiscale_SDE}
\begin{aligned}
dx &= adt + dW_1\\
dy &= -\frac{y}{\epsilon} dt + \frac{1}{\sqrt{\epsilon}} dW_2
\end{aligned}
\end{equation}

@@

We want to emphasize the link between multi scale SDEs and NIVs: NIVs rescales the variables so that the ``fast'' variables become small.
%
For example, in \eqref{eq:multiscale_SDE}, let $y = \frac{z}{\sqrt{\epsilon}}$. 
%
Then
\begin{equation}
\begin{aligned}
dx &= adt + dW_1\\
dz &= -\frac{z}{\epsilon} dt +  dW_2
\end{aligned}
\end{equation}

@@

Note: saturation time of SDE has to be smaller than the timescales

@@

@@

Empirical configuration/demonstration of the method, how to use the analysis to set the parameters in the algorithm.

From \eqref{eq:taylor_expansion}, we can see that the squared {\em intrinsic} distance $\| X_2 - X_1 \|^2$, is a function of $\|Y_2 - Y_1\|$ and $\delta t$. 
%
If the first term in the expansion dominates, then $\|X_2 - X_1 \|^2$ should be independent of $\delta t$, and should vary quadratically with $\| Y_2 - Y_1\|$. 
%
We can find such a regime empirically (by plotting $\| X_2 - X_1 \|^2$ as a function of $\delta t$ and $\|Y_2 - Y_1\|$), and select a kernel distance where both conditions hold.
